---
title: "Mini HW 04 - Visualizing Pokemon"
author: "Mine Cetinkaya-Rundel"
date: "Sep 7. 2017"
output: 
  html_document: 
    fig_height: 4
    highlight: pygments
    keep_md: yes
    theme: sandstone
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load required packages:

```{r load-packages, message=FALSE}
library(readr)
library(ggplot2)
library(dplyr)
```

## Data

Load data:

```{r load-data, message=FALSE}
pokemon <- read_csv("data/pokemon.csv")
```

View the data:

```{r}
pokemon
```


## Analysis

### Task 1: 

*Pick two numerical variables and use a scatterplot to visualize their relationship.*

```{r name-me-im-a-chunk}

```


### Task 2: 

*Pick a third categorical variable, and color the points on the scatterplot by levels of this variable.*

```{r me-too}

```

### Task 3: 

*Pick two categorical variables and make a bar plot that depicts the relationship between them.*

```{r same-here}

```

### Task 4: 

*Pick a numerical and a categorical variable, and construct side-by-side box plots depicting the relationship between them.*

```{r gotta-name-em-all}

```

### Task 5: 

*Learn something new: violin plots! Read about them at http://ggplot2.tidyverse.org/reference/geom_violin.html, and convert your side-by-side box plots from the previous task to violin plots.*

```{r whats-in-a-name}

```

